Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-21 paper.qmd
Added table position for link table

The digit 1 of **Hand-written digits** data shows how the model accurately capture the non-linear structure. Also, twisted pattern of the model evident that

example further illustrates the model's ability to accurately capture non-linear structures and provide additional information. Key findings include a twisted pattern that compresses the structure in some projections and long line segments that detect anomalies.

@@

```{r}
#| label: tbl-links
#| tbl-cap: "Example videos."

>>>>

The digit 1 of **Hand-written digits** data shows how the model accurately capture the non-linear structure. Not only that, the \pD{} model error help to find the anomalies of digit 1 images. Also, twisted pattern of the model evident that how tSNE tries to maintain the local structure by positioning the similar patterns of digit 1 close to each other.

@@

```{r}
#| label: tbl-links
#| tbl-cap: "Example videos."
#| tbl-pos: H
